### 2024-05-18 fantasy-football.qmd
20240518 - move content
20240518 - add video introductions
20240518 - table captions

@@

@@

@@

@@

@@

@@

>>>>

Here is a video that provides a brief introduction to American football:

@@

Here is a video that provides a brief introduction to fantasy football:

@@

: Offensive Players in the Starting Lineup {#tbl-lineupOffense tbl-colwidths="[25,75]"}

@@

: Common Scoring Settings for Offensive Players {#tbl-scoringOffense tbl-colwidths="[75,25]"}

@@

: Common Scoring Settings for Kickers {#tbl-scoringKickers tbl-colwidths="[75,25]"}

@@

: Common Scoring Settings for Team Defense/Special Teams {#tbl-scoringDST tbl-colwidths="[75,25]"}

@@

: Common Scoring Settings for Individual Defensive Players {#tbl-scoringIDP tbl-colwidths="[75,25]"}
